Fast Sorting on Modern Computers

### 2007-01-29 docs/tech_report/radix.tex
did the abstract. removed comment from the latex files
Updated the tech report to revision 1, which corrects 16 to 20. This also fixes the graphs in some places.

\label{radix}
%\section{Description}

@@

The number of iterations across the array is constant, however, proportional to
$(bitsPerInt/log_2(Radix))$. For a 32-bit integer and a radix of 256, this is
four steps and each step has four passes over the array, for a total of 16
passes over the array. With eight keys per cache line, there should be about two
misses per key, when the array doesn't fit into the array, though this depends
on the placing of the auxiliary array.

@@

Due to the reduced copying, memory-tuned radixsort should have a lower
instruction count and fewer cache misses that base radixsort. There should be
nine passes over the array, leading to just over one miss per key, as opposed to
two misses per key with base radixsort. The complexity and branch prediction
results should remain the same. The instruction count should, however, reduce by
nearly a half to $\frac{9}{16}^{th}s$ of base radixsort.

@@

Also, in both cases in LaMarca's graphs, once the array no longer fits in the
cache, the number of misses jumps to around 3.25 (which would be equivalent to
1.625 misses per key in our results), where they stay. Our results
disagree, showing approximately 2.5 misses per key for base radixsort.

>>>>

\label{radix}

@@

The number of iterations across the array is constant, however, proportional to
$(bitsPerInt/log_2(Radix))$. For a 32-bit integer and a radix of 256, this is
four steps and each step has five passes over the array, for a total of 20
passes over the array. With eight keys per cache line, there should be about 2.5
misses per key, when the array doesn't fit into the array, though this depends
on the placing of the auxiliary array.

@@

Due to the reduced copying, memory-tuned radixsort should have a lower
instruction count and fewer cache misses that base radixsort. There should be
nine passes over the array, leading to just over one miss per key, as opposed to
two misses per key with base radixsort. The complexity and branch prediction
results should remain the same. The instruction count should, however, reduce by
nearly a half to $\frac{9}{20}^{th}s$ of base radixsort.

@@

Also, in both cases in LaMarca's graphs, once the array no longer fits in the
cache, the number of misses jumps to around 3.25 (which would be equivalent to
1.625 misses per key in our results), where they stay. Our results disagree,
showing approximately 2.5 misses per key for base radixsort, in line with our
predictions.
